|

### 2022-01-31 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
paper
remove distrib warning

---
title: |
  | DRAFT, NOT FOR DISTRIBUTION 
  | Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises
author:
  - Rex W. Douglass^[Department of Political Science, University of California, San Diego, CA, USA.]
  - Thomas Leo Scherer^[Department of Political Science, University of California, San Diego, CA, USA.]
  - J. Andrés Gannon^[Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.]
  - Erik Gartzke^[Department of Political Science, University of California, San Diego, CA, USA.]
  - Jon Lindsay^[School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.]
  - Shannon Carcelli^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - Jonathan Wilkenfeld^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - David M. Quinn^[Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.]
  - Catherine Aiken^[Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.]
  - Jose Miguel Cabezas Navarro^[Society and Health Research Center, Universidad Mayor, Santiago, Chile.]
  - Neil Lund^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - Egle Murauskaite^[ICONS Project // START,  University of Maryland, College Park, MD, USA.]
  - Diana Partridge^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]

@@

TLS = TRUE
```

>>>>

---
title: |
  | Introducing the ICBe Dataset: Very High Recall and Precision Event Extraction from Narratives about International Crises
author:
  - Rex W. Douglass^[Department of Political Science, University of California, San Diego, CA, USA.]
  - Thomas Leo Scherer^[Department of Political Science, University of California, San Diego, CA, USA.]
  - J. Andrés Gannon^[Belfer Center for Science and International Affairs, Harvard Kennedy School, MA, USA.]
  - Erik Gartzke^[Department of Political Science, University of California, San Diego, CA, USA.]
  - Jon Lindsay^[School of Cybersecurity and Privacy | Sam Nunn School of International Affairs, Georgia Institute of Technology, GA, USA.]
  - Shannon Carcelli^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - Jonathan Wilkenfeld^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - David M. Quinn^[Faculty Specialist, National Consortium for the Study of Terrorism and Responses to Terrorism (START), University of Maryland, College Park, MD, USA.]
  - Catherine Aiken^[Edmund A. Walsh School of Foreign Service, Georgetown University, Washington, DC, USA.]
  - Jose Miguel Cabezas Navarro^[Society and Health Research Center, Universidad Mayor, Santiago, Chile.]
  - Neil Lund^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]
  - Egle Murauskaite^[ICONS Project // START,  University of Maryland, College Park, MD, USA.]
  - Diana Partridge^[Department of Government and Politics, University of Maryland, College Park, MD, USA.]

@@

TLS = FALSE
```
